---
title: 'Investigating Significance II: v3'
author: "Ben Wheeler"
date: "April 6, 2017"
output:
  html_notebook: default
  pdf_document: default
---
####Investigating All Candidates in a Race as a single population
update: 10-23-2017
* Updated observation columns for variables. (111-117) instead of 89-
update: 10-27-2017
* Updated bottom of analysis for Spearman-Ranking Correlation, included ggplot2.
* Including Attempts to normalize Percentage Data.

##Purpose
The purpose of this document is to make progress in determining significance of Twitter Percentages for Republicans.
This analysis uses a different data structure than we have been using, it takes advantage of using each candidate as a single observation, but treats all candidates in all counties as a population. There are 62 counties in New York, of them all of them had tweets that were placed within their boundaries. This dataset includes 62 observations for each candidate. One observation for each county. Thus the republican dataset includes 186 observations.

##Key Takeaways
* All Subsets are significant when run with any characteristics.
* The population is significant, however the individuals are not.
* Is the population significant because of underlying issues with using everyone from the same race, aka they are all reliant on each other.  I still can't answer this question.

##Determine ability to use Linear Regression
#####Assumptions are as follows:
* Linear relationship
* Multivariate normality
* No or little multicollinearity
* No auto-correlation
* Homoscedasticity

Also there is a rule of thumb of 20 records in order to conduct linear regression. 
http://www.statisticssolutions.com/assumptions-of-linear-regression/

http://www.sthda.com/english/wiki/correlation-test-between-two-variables-in-r
  - Checking the Correlation between two variables, how do I test the correlation...
  - potentially use rank() to rank and then do a rho or a spearman correlation.

####Read in file
```{r}
x ='C:\\Temp\\FINAL_INPUTS\\Box Sync\\R\\v3'
setwd(x)

d3 <- read.table(paste(getwd()[1],"v3_AllTags_002_AllSources_analysis_v3_310.csv",sep = '/'),
                 header=TRUE, sep=",", na.strings="NA", dec=".", strip.white=TRUE)
```


####Subset Republicans
The below code subsets the candidates for plotting and additional testing.

```{r subset data}
RepTKC <- subset(d3,d3$CANDIDATE == 'TRUMP' | d3$CANDIDATE == 'KASICH' | d3$CANDIDATE == 'CRUZ')
RepTK  <- subset(d3,d3$CANDIDATE == 'TRUMP'  | d3$CANDIDATE == 'KASICH')
RepCK  <- subset(d3,d3$CANDIDATE == 'KASICH' | d3$CANDIDATE == 'CRUZ')
RepTC  <- subset(d3,d3$CANDIDATE == 'TRUMP'  | d3$CANDIDATE == 'CRUZ')

RepT <- subset(d3,d3$CANDIDATE == 'TRUMP')
RepK <- subset(d3,d3$CANDIDATE == 'KASICH')
RepC <- subset(d3,d3$CANDIDATE == 'CRUZ')

```

####Define Function to Print out Statistics and Plot Data

```{r}
gloop <- function(n,data.in,subset1,subset2,subset3,label.main,label.X, label.Y){
    RegModel.Model <- lm(Candidate_VS~data.in[,n], data=data.in)
    Test <- summary(RegModel.Model)
    Coef  <- Test[4]
    rvals <- c(Test[9],Test[8])
    xlim <- c(0,1)
    ylim <- c(0,1)
      plot(subset1$Candidate_VS,subset1[,n],xlim=xlim, ylim=ylim, col='Blue',
           xlab=label.X,
           ylab =label.Y,
           main = label.main)
      points(subset2$Candidate_VS,subset2[,n],xlim=xlim, ylim=ylim, col='Green')
      points(subset3$Candidate_VS,subset3[,n],xlim=xlim, ylim=ylim, col='Red')
      legend("right", 
             legend=c("Trump", "Kasich","Cruz"),
                col=c("blue","Green","red"), 
                pch=1, cex=0.8, inset =.01, box.lty=1)
      var1 <- substr(toString(rvals[2]),1,5)
      var2 <- substr(toString(rvals[1]),1,5)
      text(0.95,0.05,label=paste("R2:",var1))
      text(0.923,0.1,label=paste("R2_adj:",var2))
    return(list(
      stats=c(Coef,rvals),
      model=RegModel.Model
    ))      
}

gloop2 <- function(n,data.in,subset1,subset2,label.main,label.X, label.Y,cand1,cand2){
    RegModel.Model <- lm(Candidate_VS~data.in[,n], data=data.in)
    Test <- summary(RegModel.Model)
    Coef  <- Test[4]
    rvals <- c(Test[9],Test[8])
    xlim <- c(0,1)
    ylim <- c(0,1)
      plot(subset1$Candidate_VS,subset1[,n],xlim=xlim, ylim=ylim, col='Blue',
           xlab=label.X,
           ylab =label.Y,
           main = label.main)
      points(subset2$Candidate_VS,subset2[,n],xlim=xlim, ylim=ylim, col='Red')
      legend("right", 
             legend=c(cand1, cand2),
                col=c("blue","red"), 
                pch=1, cex=0.8, inset =.01, box.lty=1)
      var1 <- substr(toString(rvals[2]),1,5)
      var2 <- substr(toString(rvals[1]),1,5)
      text(0.95,0.05,label=paste("R2:",var1))
      text(0.923,0.1,label=paste("R2_adj:",var2))
    return(list(
      stats=c(Coef,rvals),
      model=RegModel.Model
    ))      
}
```




#Outcomes
```{r}
d17 <- gloop(111,RepTKC,RepT,RepK,RepC,"17th","VoteShare","TweetShare")
d17$stats

d18 <- gloop(112,RepTKC,RepT,RepK,RepC,"18th","VoteShare","TweetShare")
d18$stats

d19b4 <- gloop(113,RepTKC,RepT,RepK,RepC,"19th Before Election Called","VoteShare","TweetShare")
d19b4$stats

d19aft <- gloop(114,RepTKC,RepT,RepK,RepC,"19th After Election Called","VoteShare","TweetShare")
d19aft$stats

d20 <- gloop(115,RepTKC,RepT,RepK,RepC,"20th","VoteShare","TweetShare")
d20$stats

db4 <- gloop(116,RepTKC,RepT,RepK,RepC,"All Tweets Before Election Called","VoteShare","TweetShare")
db4$stats

dall <- gloop(117,RepTKC,RepT,RepK,RepC,"All Tweets","VoteShare","TweetShare")
dall$stats

```

# Trump and Kasich Only
This section looks at R-squared values for TweetShare vs. VoteShare after removing Cruz.

```{r}
d17 <- gloop2(111,RepTK,RepT,RepK,"17th","VoteShare","TweetShare","Trump","Kasich")
d17$stats

d18 <- gloop2(112,RepTK,RepT,RepK,"18th","VoteShare","TweetShare","Trump","Kasich")
d18$stats

d19b4 <- gloop2(113,RepTK,RepT,RepK,"19th Before Election Called","VoteShare","TweetShare","Trump","Kasich")
d19b4$stats

d19aft <- gloop2(114,RepTK,RepT,RepK,"19th After Election Called","VoteShare","TweetShare","Trump","Kasich")
d19aft$stats

d20 <- gloop2(115,RepTK,RepT,RepK,"20th","VoteShare","TweetShare","Trump","Kasich")
d20$stats

db4 <- gloop2(116,RepTK,RepT,RepK,"All Tweets Before Election Called","VoteShare","TweetShare","Trump","Kasich")
db4$stats

db4 <- gloop2(117,RepTK,RepT,RepK,"All Tweets","VoteShare","TweetShare","Trump","Kasich")
db4$stats

```

# Trump and Cruz Only
This section looks at R-squared values for TweetShare vs. VoteShare after removing Cruz.

```{r}
d17 <- gloop2(111,RepTC,RepT,RepC,"17th","VoteShare","TweetShare","Trump","Cruz")
d17$stats

d18 <- gloop2(112,RepTC,RepT,RepC,"18th","VoteShare","TweetShare","Trump","Cruz")
d18$stats

d19b4 <- gloop2(113,RepTC,RepT,RepC,"19th Before Election Called","VoteShare","TweetShare","Trump","Cruz")
d19b4$stats

d19aft <- gloop2(114,RepTC,RepT,RepC,"19th After Election Called","VoteShare","TweetShare","Trump","Cruz")
d19aft$stats

d20 <- gloop2(115,RepTC,RepT,RepC,"20th","VoteShare","TweetShare","Trump","Cruz")
d20$stats

db4 <- gloop2(116,RepTC,RepT,RepC,"All Tweets Before Election Called","VoteShare","TweetShare","Trump","Cruz")
db4$stats

db4 <- gloop2(85,RepTC,RepT,RepC,"All Tweets","VoteShare","TweetShare","Trump","Cruz")
db4$stats

```

#Kasich and Cruz Only
This analysis looks at any correlation that exists using only Kasich and Cruz, it lacks any significant outcomes.

```{r}
d17 <- gloop2(111,RepCK,RepK,RepC,"17th","VoteShare","TweetShare","Kasich","Cruz")
d17$stats

d18 <- gloop2(112,RepCK,RepK,RepC,"18th","VoteShare","TweetShare","Kasich","Cruz")
d18$stats

d19b4 <- gloop2(113,RepCK,RepK,RepC,"19th Before Election Called","VoteShare","TweetShare","Kasich","Cruz")
d19b4$stats

d19aft <- gloop2(114,RepCK,RepK,RepC,"19th After Election Called","VoteShare","TweetShare","Kasich","Cruz")
d19aft$stats

d20 <- gloop2(115,RepCK,RepK,RepC,"20th","VoteShare","TweetShare","Kasich","Cruz")
d20$stats

db4 <- gloop2(116,RepCK,RepK,RepC,"All Tweets Before Election Called","VoteShare","TweetShare","Kasich","Cruz")
db4$stats

db4 <- gloop2(117,RepCK,RepK,RepC,"All Tweets","VoteShare","TweetShare","Kasich","Cruz")
db4$stats

```


```{r Spearman-Ranking Correlation}
RepTKC$rank_TS17 <- rank(RepTKC$Candidate_TS17)
RepTKC$rank_VS <- rank(RepTKC$Candidate_VS)

cor(RepTKC$rank_VS,RepTKC$rank_TS17, method = 'spearman')

RepTKC$rank_TS18 <- rank(RepTKC$Candidate_TS18)
cor(RepTKC$rank_VS,RepTKC$rank_TS18, method = 'spearman')

RepTKC$rank_TS19b4 <- rank(RepTKC$Candidate_TS19b4)
cor(RepTKC$rank_VS,RepTKC$rank_TS19b4, method = 'spearman')

RepTKC$rank_TS <- rank(RepTKC$Candidate_TS)


library(ggplot2)
ggplot(data=RepTKC, aes(rank_VS, rank_TS19b4 , colour = CANDIDATE))  + geom_point()
  
ggplot(data=RepTKC, aes(rank_VS, rank_TS , colour = CANDIDATE))  + geom_point()
```

```{r Normalizing and AutoCorrelation}
hist(RepTKC$Candidate_TS)
hist(RepK$Candidate_TS)
hist(RepC$Candidate_TS)
hist(RepT$Candidate_TS)

# Test Autocorrelation
#library(car)
#Model.All <-  lm(Candidate_VS~Candidate_TS, data=RepTKC)
#RegModel.CandidateT <- lm(Candidate_VS~Candidate_TS17, data=RepT)
#durbinWatsonTest(Model.All)
getwd()[1]
iit <- read.csv(.\)
```


```{r BaselevelModels, include=FALSE}
# These models are to be run to test for specific things. 
RegModel.Candidate <- lm(Candidate_VS~Candidate_TS, data=d3)
RegModel.Candidate17 <- lm(Candidate_VS~Candidate_TS17, data=d3)
RegModel.Candidate18 <- lm(Candidate_VS~Candidate_TS18, data=d3)
RegModel.Candidate19aft_u <- lm(Candidate_VS~Candidate_TS19aft_u, data=d3)
RegModel.Candidate19b4 <- lm(Candidate_VS~Candidate_TS19b4, data=d3)
RegModel.Candidate20 <- lm(Candidate_VS~Candidate_TS20, data=d3)
RegModel.Candidate_b4 <- lm(Candidate_VS~Candidate_TS_b4, data=d3)

```