---
title: "OLS Model"
output: html_notebook
---
This Script writes out the resultant Stepwise Models from 11 different datasets using the same inputs.

```{r}
options("scipen" = 100)

x ='C:/Temp/FINAL_INPUTS/Box Sync/R/v4'
setwd(x)

d3 <- read.table(paste(getwd()[1],"v3_AllTags_002_AllSources_analysis_v3_310.csv",sep = '/'),
                 header=TRUE, sep=",", na.strings="NA", dec=".", strip.white=TRUE)
```
```{r subset data}
d3$PopDens <- log(d3$TotPop/d3$SqMiles)
d3$perc_white_comb <- d3$White_and_combination/d3$TotPop
d3$perc_white <- d3$White_only/d3$TotPop
d3$perc_Fem <- d3$FemOver18/d3$PopOver18

#Republicans
RepTKC <- subset(d3,d3$CANDIDATE == 'TRUMP' | d3$CANDIDATE == 'KASICH' | d3$CANDIDATE == 'CRUZ')
RepTK  <- subset(d3,d3$CANDIDATE == 'TRUMP'  | d3$CANDIDATE == 'KASICH')
RepCK  <- subset(d3,d3$CANDIDATE == 'KASICH' | d3$CANDIDATE == 'CRUZ')
RepTC  <- subset(d3,d3$CANDIDATE == 'TRUMP'  | d3$CANDIDATE == 'CRUZ')

RepT <- subset(d3,d3$CANDIDATE == 'TRUMP')
RepK <- subset(d3,d3$CANDIDATE == 'KASICH')
RepC <- subset(d3,d3$CANDIDATE == 'CRUZ')

#Democrats
DemHB <- subset(d3,d3$CANDIDATE == 'HILLARY' | d3$CANDIDATE == 'BERNIE')
DemH <- subset(d3,d3$CANDIDATE == 'HILLARY')
DemB <- subset(d3,d3$CANDIDATE == 'BERNIE')

```

Thus Far there have been several findings, for all republicans grouped together in a single analysis, these have been descriptive models for producing  significant results.
These models remove the variables that include number counts after the election was announced, these while significant, are skewed based on likely news/gloating over victory, which would increase victor tweets and decrease the tweets of the subjugated. These relationships were regardless of the actual characteristics of the county, however, on the individual Candidate level, this is more likely to correctly reflect.

The Following Chunk will calculate all the outputs for a stepwise with the following Models
```{r builder}
DfList <- list(d3,RepTKC,RepTC,RepCK,RepTK, RepT,RepK,RepC, DemHB, DemH,DemHB)
strList<- list("d3","RepTKC","RepTC","RepCK","RepTK", "RepT","RepK","RepC", "DemHB", "DemH","DemB")
len <- 11
outputs <- list()
Formulae <- list()
NoStep <- list()
setwd(x)

for (i in 1:len){
dfor <- data.frame(DfList[i])
RegModel.Model <- lm(dfor$Candidate_VS~
                       dfor$PopDens
                    +dfor$Perc_BachelorsDeg_and_higher
                     +dfor$perc_white
                     +dfor$MedianAge_Total
                     +dfor$perc_Fem
                     +dfor$Candidate_TS17
                     +dfor$Candidate_TS18
                     +dfor$Candidate_TS19b4
                     +dfor$Candidate_TS_b4,
                     data=na.omit(dfor))
obj <- step(RegModel.Model,direction="backward",trace=FALSE)
TheChosenOne <- lm(obj$call$formula,data = dfor)
outputs[[paste(strList[i])]] <- TheChosenOne
Formulae[[paste(strList[i])]] <- obj$call$formula
NoStep[[paste(strList[i])]] <- list(summary(RegModel.Model))
}
```

```{r}

options("scipen" = 100)
setwd(x)
sink('LM.txt')
for (i in 1:len)
{
  print(strList[[i]])
  print(Formulae[[i]])
  print(summary(outputs[[i]]))
}

sink()

sink('LM_formulae_Only.txt')
for (i in 1:len)
{
  print(strList[[i]])
  print(Formulae[[i]])
}
sink()

sink('LM_formulae_Only_noSTEP.txt')
for (i in 1:len)
{
  print(NoStep[[i]])
}
sink()

```

```{r}
Bernie <- lm(DemB$Candidate_VS ~ DemB$PopDens + DemB$Candidate_TS_b4 + DemB$perc_Fem, data=DemB)
summary(Bernie)
```

```{r}
library(forecast)
cvmod <- CV(Bernie)
```

