---
title: "Spearman's Correlation Test - Republicans"
author: "Ben Wheeler"
date: "October 29, 2017"
output:
  html_notebook: default
  pdf_document: default
---
This document is the proper workspace to start reporting out Spearman's Rho's.

####Read in file
Set `x` equal to the directory in which the raw '310' input file exists.
```{r}
x ='C:\\Temp\\FINAL_INPUTS\\Box Sync\\R\\v4'
setwd(x)

d3 <- read.table(paste(getwd()[1],"v3_AllTags_002_AllSources_analysis_v3_310.csv",sep = '/'),
                 header=TRUE, sep=",", na.strings="NA", dec=".", strip.white=TRUE)
```

####Subset Republicans
The below code subsets the candidates for plotting and additional testing.

```{r subset data}
RepTKC <- subset(d3,d3$CANDIDATE == 'TRUMP' | d3$CANDIDATE == 'KASICH' | d3$CANDIDATE == 'CRUZ')
RepTK  <- subset(d3,d3$CANDIDATE == 'TRUMP'  | d3$CANDIDATE == 'KASICH')
RepCK  <- subset(d3,d3$CANDIDATE == 'KASICH' | d3$CANDIDATE == 'CRUZ')
RepTC  <- subset(d3,d3$CANDIDATE == 'TRUMP'  | d3$CANDIDATE == 'CRUZ')

RepT <- subset(d3,d3$CANDIDATE == 'TRUMP')
RepK <- subset(d3,d3$CANDIDATE == 'KASICH')
RepC <- subset(d3,d3$CANDIDATE == 'CRUZ')

```

####gloop adaptation
The purpose of this is to import the g{raph}loop function and alter it.
`gloop_spearman` function written to include new sets called Candidate_VS_RANK which should re-calculate each time the function is run. Ranks should ve calculated for the input data and mapped to Ranktest column

* write up Spearman read out.
* write up 

```{r}
gloop_spearman <- function(n,data.in,subset1,subset2,subset3,label.main,label.X, label.Y){
  data.in$Candidate_VS_Rank <-  rank(data.in$Candidate_VS)
  data.in$Ranktest<- rank(data.in[,n])
  spear = cor(data.in$Candidate_VS_Rank,data.in$Ranktest, method = 'spearman')
  
  
  RegModel.Model <- lm(Candidate_VS~data.in[,n], data=data.in)
    Test <- summary(RegModel.Model)
    Coef  <- Test[4]
    rvals <- c(Test[9],Test[8])
    xlim <- c(0,1)
    ylim <- c(0,1)
      plot(subset1[,n],subset1$Candidate_VS,xlim=xlim, ylim=ylim, col='Blue',
           xlab=label.X,
           ylab =label.Y,
           main = label.main)
      points(subset2[,n],subset2$Candidate_VS,xlim=xlim, ylim=ylim, col='Green')
      points(subset3[,n],subset3$Candidate_VS,xlim=xlim, ylim=ylim, col='Red')
      legend("right", 
             legend=c("Trump", "Kasich","Cruz"),
                col=c("blue","Green","red"), 
                pch=1, cex=0.8, inset =.01, box.lty=1)
      var1 <- substr(toString(rvals[2]),1,5)
      var2 <- substr(toString(rvals[1]),1,5)
      text(0.95,0.05,label=paste("R2:",var1))
      text(0.923,0.1,label=paste("R2_adj:",var2))
    return(list(
      stats=c(Coef,rvals),
      model=RegModel.Model,
      s=spear
    ))      
}

gloop2_spearman <- function(n,data.in,subset1,subset2,label.main,label.X, label.Y,cand1,cand2){
  data.in$Candidate_VS_Rank <-  rank(data.in$Candidate_VS)
  data.in$Ranktest<- rank(data.in[,n])
  spear = cor(data.in$Candidate_VS_Rank,data.in$Ranktest, method = 'spearman')
  
  RegModel.Model <- lm(Candidate_VS~data.in[,n], data=data.in)
    Test <- summary(RegModel.Model)
    Coef  <- Test[4]
    rvals <- c(Test[9],Test[8])
    xlim <- c(0,1)
    ylim <- c(0,1)
      plot(subset1$Candidate_VS,subset1[,n],xlim=xlim, ylim=ylim, col='Blue',
           xlab=label.X,
           ylab =label.Y,
           main = label.main)
      points(subset2$Candidate_VS,subset2[,n],xlim=xlim, ylim=ylim, col='Red')
      legend("right", 
             legend=c(cand1, cand2),
                col=c("blue","red"), 
                pch=1, cex=0.8, inset =.01, box.lty=1)
      var1 <- substr(toString(rvals[2]),1,5)
      var2 <- substr(toString(rvals[1]),1,5)
      text(0.95,0.05,label=paste("R2:",var1))
      text(0.923,0.1,label=paste("R2_adj:",var2))
    return(list(
      stats=c(Coef,rvals),
      model=RegModel.Model,
      s=spear
    ))      
}

gloop3_spearman <- function(n,data.in,subset1,subset2,label.main,label.X, label.Y,cand1,cand2)
  {
  data.in$Candidate_VS_Rank <-  rank(data.in$Candidate_VS)
  data.in$Ranktest<- rank(data.in[,n])
  spear = cor(data.in$Candidate_VS_Rank,data.in$Ranktest, method = 'spearman')
 
  return(list(
      stats=c(Coef,rvals),
      model=RegModel.Model,
      s=spear))
}
  
```

```{r test gloop}
d17 <- gloop_spearman(111,RepTKC,RepT,RepK,RepC,"17th","TweetShare","VoteShare")
d18 <- gloop_spearman(112,RepTKC,RepT,RepK,RepC,"18th","TweetShare","VoteShare")
d19b4 <- gloop_spearman(113,RepTKC,RepT,RepK,RepC,"19th Before Election Called","TweetShare","VoteShare")
d19aft <- gloop_spearman(114,RepTKC,RepT,RepK,RepC,"19th After Election Called","TweetShare","VoteShare")
d20 <- gloop_spearman(115,RepTKC,RepT,RepK,RepC,"20th","TweetShare","VoteShare")
db4 <- gloop_spearman(116,RepTKC,RepT,RepK,RepC,"All Tweets Before Election Called","TweetShare","VoteShare")
dall <- gloop_spearman(117,RepTKC,RepT,RepK,RepC,"All Tweets","TweetShare","VoteShare")

p1 <- c("TS17","TS18","TS19_b4","TS19_aft","TS20","db4","TS")
p2 <- c(d17$s,d18$s,d19b4$s,d19aft$s,d20$s,db4$s,dall$s)

df_original <- data.frame(p1,p2)
df_original
df_transpose = t(df_original)
df_transpose

```

####Attempt at For Loop
The Below section is meant to cycle through the three groupings for the republicans, potentially all the remaining variables, that way we can just update for each segment.

This section I am struggling to make gloop2 or gloop3 spearman work.
```{r test gloop as loop}
c <- list(RepTC,RepCK,RepTK)
vars <- rbind.data.frame(
    c("RepT","RepC","Trump","Cruz"), 
    c("RepC","RepK","Cruz","Kasich"), 
    c("RepT","RepK","Trump","Kasich")
)


for (i in 1:3){
  d17 <- gloop3_spearman(111,c[i],get(paste(vars[i,1])),get(paste(vars[i,2])),"17th","TweetShare","VoteShare",get(paste(vars[i,3])),get(paste(vars[i,4])))
  d18 <- gloop3_spearman(112,c[i],get(paste(vars[i,1])),get(paste(vars[i,2])),"18th","TweetShare","VoteShare",get(paste(vars[i,3])),get(paste(vars[i,4])))
  d19b4 <- gloop3_spearman(113,c[i],get(paste(vars[i,1])),get(paste(vars[i,2])),"19th Before Election Called","TweetShare","VoteShare",get(paste(vars[i,3])),get(paste(vars[i,4])))
  d19aft <- gloop3_spearman(114,c[i],get(paste(vars[i,1])),get(paste(vars[i,2])),"19th After Election Called","TweetShare","VoteShare",get(paste(vars[i,3])),get(paste(vars[i,4])))
  d20 <- gloop3_spearman(115,c[i],get(paste(vars[i,1])),get(paste(vars[i,2])),"20th","TweetShare","VoteShare",get(paste(vars[i,3])),get(paste(vars[i,4])))
  db4 <- gloop3_spearman(116,c[i],get(paste(vars[i,1])),get(paste(vars[i,2])),"All Tweets Before Election Called","TweetShare","VoteShare",get(paste(vars[i,3])),get(paste(vars[i,4])))
  dall <- gloop3_spearman(117,c[i],get(paste(vars[i,1])),get(paste(vars[i,2])),"All Tweets","TweetShare","VoteShare",get(paste(vars[i,3])),get(paste(vars[i,4])))
  }


p1 <- c("TS17","TS18","TS19_b4","TS19_aft","TS20","db4","TS")
p2 <- c(d17$s,d18$s,d19b4$s,d19aft$s,d20$s,db4$s,dall$s)

df_original <- data.frame(p1,p2)
df_original
df_transpose = t(df_original)
df_transpose

```



```{r output}
output
write.csv(df_transpose,paste(getwd()[1],"Spearman_CorrelationCoef.csv",sep = '/'),
          append = FALSE, quote = TRUE, sep = ",",
          eol = "\n", na = "NA", dec = ".", row.names = TRUE,
          col.names = TRUE, qmethod = c("escape", "double"),
          fileEncoding = "")

```
