---
title: "Spearman's Correlation Test - Republicans"
author: "Ben Wheeler"
date: "October 29, 2017"
output:
  html_notebook: default
  pdf_document: default
---
This document is the proper workspace to start reporting out Spearman's Rho's.

####Read in file
Set `x` equal to the directory in which the raw '310' input file exists.
```{r}
x ='C:\\Temp\\FINAL_INPUTS\\Box Sync\\R\\v4'
setwd(x)

d3 <- read.table(paste(getwd()[1],"v3_AllTags_002_AllSources_analysis_v3_310.csv",sep = '/'),
                 header=TRUE, sep=",", na.strings="NA", dec=".", strip.white=TRUE)
```

####Subset Republicans
The below code subsets the candidates for plotting and additional testing.

```{r subset data}
RepTKC <- subset(d3,d3$CANDIDATE == 'TRUMP' | d3$CANDIDATE == 'KASICH' | d3$CANDIDATE == 'CRUZ')
RepTK  <- subset(d3,d3$CANDIDATE == 'TRUMP'  | d3$CANDIDATE == 'KASICH')
RepCK  <- subset(d3,d3$CANDIDATE == 'KASICH' | d3$CANDIDATE == 'CRUZ')
RepTC  <- subset(d3,d3$CANDIDATE == 'TRUMP'  | d3$CANDIDATE == 'CRUZ')

RepT <- subset(d3,d3$CANDIDATE == 'TRUMP')
RepK <- subset(d3,d3$CANDIDATE == 'KASICH')
RepC <- subset(d3,d3$CANDIDATE == 'CRUZ')

```

####gloop adaptation
The purpose of this is to import the g{raph}loop function and alter it.
`gloop_spearman` function written to include new sets called Candidate_VS_RANK which should re-calculate each time the function is run. Ranks should ve calculated for the input data and mapped to Ranktest column

* write up Spearman read out.
* write up 

```{r}
gloop_spearman <- function(n,data.in,subset1,subset2,subset3,label.main,label.X, label.Y){
  data.in$Candidate_VS_Rank <-  rank(data.in$Candidate_VS)
  data.in$Ranktest<- rank(data.in[,n])
  spear = cor(data.in$Candidate_VS_Rank,data.in$Ranktest, method = 'spearman')
  
  
  RegModel.Model <- lm(Candidate_VS~data.in[,n], data=data.in)
    Test <- summary(RegModel.Model)
    Coef  <- Test[4]
    rvals <- c(Test[9],Test[8])
    xlim <- c(0,1)
    ylim <- c(0,1)
      plot(subset1[,n],subset1$Candidate_VS,xlim=xlim, ylim=ylim, col='Blue',
           xlab=label.X,
           ylab =label.Y,
           main = label.main)
      points(subset2[,n],subset2$Candidate_VS,xlim=xlim, ylim=ylim, col='Green')
      points(subset3[,n],subset3$Candidate_VS,xlim=xlim, ylim=ylim, col='Red')
      legend("right", 
             legend=c("Trump", "Kasich","Cruz"),
                col=c("blue","Green","red"), 
                pch=1, cex=0.8, inset =.01, box.lty=1)
      var1 <- substr(toString(rvals[2]),1,5)
      var2 <- substr(toString(rvals[1]),1,5)
      text(0.95,0.05,label=paste("R2:",var1))
      text(0.923,0.1,label=paste("R2_adj:",var2))
    return(list(
      stats=c(Coef,rvals),
      model=RegModel.Model,s=spear
    ))      
}

gloop2 <- function(n,data.in,subset1,subset2,label.main,label.X, label.Y,cand1,cand2){
    RegModel.Model <- lm(Candidate_VS~data.in[,n], data=data.in)
    Test <- summary(RegModel.Model)
    Coef  <- Test[4]
    rvals <- c(Test[9],Test[8])
    xlim <- c(0,1)
    ylim <- c(0,1)
      plot(subset1$Candidate_VS,subset1[,n],xlim=xlim, ylim=ylim, col='Blue',
           xlab=label.X,
           ylab =label.Y,
           main = label.main)
      points(subset2$Candidate_VS,subset2[,n],xlim=xlim, ylim=ylim, col='Red')
      legend("right", 
             legend=c(cand1, cand2),
                col=c("blue","red"), 
                pch=1, cex=0.8, inset =.01, box.lty=1)
      var1 <- substr(toString(rvals[2]),1,5)
      var2 <- substr(toString(rvals[1]),1,5)
      text(0.95,0.05,label=paste("R2:",var1))
      text(0.923,0.1,label=paste("R2_adj:",var2))
    return(list(
      stats=c(Coef,rvals),
      model=RegModel.Model
    ))      
}
```

```{r test gloop}
d17 <- gloop_spearman(111,RepTKC,RepT,RepK,RepC,"17th","TweetShare","VoteShare")
d18 <- gloop_spearman(112,RepTKC,RepT,RepK,RepC,"18th","TweetShare","VoteShare")
d19b4 <- gloop_spearman(113,RepTKC,RepT,RepK,RepC,"19th Before Election Called","TweetShare","VoteShare")
d19aft <- gloop_spearman(114,RepTKC,RepT,RepK,RepC,"19th After Election Called","TweetShare","VoteShare")
d20 <- gloop_spearman(115,RepTKC,RepT,RepK,RepC,"20th","TweetShare","VoteShare")
db4 <- gloop_spearman(116,RepTKC,RepT,RepK,RepC,"All Tweets Before Election Called","TweetShare","VoteShare")
dall <- gloop_spearman(117,RepTKC,RepT,RepK,RepC,"All Tweets","TweetShare","VoteShare")

p1 <- c("TS17","TS18","TS19_b4","TS19_aft","TS20","db4","TS")
p2 <- c(d17$s,d18$s,d19b4$s,d19aft$s,d20$s,db4$s,dall$s)

df_original <- data.frame(p1,p2)
df_original
df_transpose = t(df_original)
df_transpose

```

```{r output}
output
write.csv(df_transpose,paste(getwd()[1],"Spearman_CorrelationCoef.csv",sep = '/'),
          append = FALSE, quote = TRUE, sep = ",",
          eol = "\n", na = "NA", dec = ".", row.names = TRUE,
          col.names = TRUE, qmethod = c("escape", "double"),
          fileEncoding = "")

```
